---
title: "The Fair Side of Chance: How Uncertainty, Power and Fairness Impact Strategic Behavior"
output: html_notebook
---

## Overview
The following analysis was conducted as part of "BDS-588 by "Fair Side of Chance" experiment conducted by Andrew Cullen, Steven Jacobs and Jordan Selesnick.

Data was collected on April 13, 2022 using mTurk.

## Data Cleaning

Below, we clean our data.

### Read in data

```{r}
library(haven)
library(tidyverse)
library(rstatix)
library(gt)
library(sjPlot)
library(ggpubr)
library(ggplot2)
library(lme4)

rm(list=ls())
data00 <- read_sav("finaldata_041522.sav")
```

### Remove participants

Participants were removed based on the following criteria:

* Did not finish
* Failed attention checks
* Failed bot check

```{r}
data01 <- data00 %>% 
  filter(Attention_Check_2_1 == 4) %>% 
  filter(!grepl('Warning:', timeOutLog)) %>%
  select(!contains("Click")) %>% 
  select(!contains("Submit")) #%>% 
 # select(Duration__in_seconds_, ResponseId, cont1:cont8,
  #       cont1.0:cont8.0, Fairness_1__1:Comments, studyID, groupID,
  #       participantRole, timeOutLog, totalPayoff, ownContribution1,
  #       a1, b1, sum1, share1:payoff8)
```

### Rename Vars

Simple transforming of variables to more managable output.

```{r}
data02 <- data01 %>%
  select(ResponseId, cont1.0:cont8.0) %>% 
  rename(cont1 = cont1.0,
         cont2 = cont2.0,
         cont3 = cont3.0,
         cont4 = cont4.0,
         cont5 = cont5.0,
         cont6 = cont6.0,
         cont7 = cont7.0,
         cont8 = cont8.0) %>% 
  filter(!is.na(cont1))

data02_02 <- data01 %>%
  select(ResponseId, cont1.1:cont8.1) %>% 
  rename(cont1 = cont1.1,
         cont2 = cont2.1,
         cont3 = cont3.1,
         cont4 = cont4.1,
         cont5 = cont5.1,
         cont6 = cont6.1,
         cont7 = cont7.1,
         cont8 = cont8.1) %>% 
  filter(!is.na(cont1))

data02_03 <- data01 %>%
  select(ResponseId, cont1.2:cont8.2) %>% 
  rename(cont1 = cont1.2,
         cont2 = cont2.2,
         cont3 = cont3.2,
         cont4 = cont4.2,
         cont5 = cont5.2,
         cont6 = cont6.2,
         cont7 = cont7.2,
         cont8 = cont8.2) %>% 
  filter(!is.na(cont1))

data02_04 <- data01 %>%
  select(ResponseId, cont1.3:cont8.3) %>% 
  rename(cont1 = cont1.3,
         cont2 = cont2.3,
         cont3 = cont3.3,
         cont4 = cont4.3,
         cont5 = cont5.3,
         cont6 = cont6.3,
         cont7 = cont7.3,
         cont8 = cont8.3) %>% 
  filter(!is.na(cont1))

data03 <- data01 %>%
  select(ResponseId, cont1:cont8) %>% 
  filter(!is.na(cont1))

data04 <- data02 %>% bind_rows(data02_02, data02_03, data02_04, data03)

data05 <- data01 %>%
  select(!(cont1:cont8)) %>% 
  select(!(cont1.0:cont8.0))  %>% 
  select(!(cont1.1:cont8.1)) %>% 
  select(!(cont1.2:cont8.2)) %>% 
  select(!(cont1.3:cont8.3)) %>% 
  left_join(data04, by = "ResponseId")  %>% 
  mutate(studyID = ifelse(is.na(studyID), 0, studyID)) %>% 
  mutate(studyID = ifelse(!is.na(Control_Statement), "Control", studyID))

#renaming "control" to ctrl // make distinct
data05 <- data05 %>% rename( ctrl_statement = Control_Statement)
```
### New Var: DVs

Create variables for mean and total contribution rate over all 8 rounds.

```{r}
      data05 <- data05 %>% 
        rowwise() %>% 
        mutate(mean_cont = mean(c_across(starts_with("cont")))) %>% 
        mutate(sum_cont = sum(c_across(starts_with("cont"))))
```

### New Var: Experimental vs. Control

Create variables that describe whether a respondent was in a control or experimental condition. This will be used in our H1 analysis later on.

```{r}
 data05 <- data05 %>% 
       mutate(ctrlvsexp = case_when(
        studyID == "PT PGG Equal Agent" ~ "experimental",
        studyID == "PT PGG Equal Systemic" ~ "experimental",
        studyID == "PT PGG Unequal Systemic" ~ "experimental",
        studyID == "PT PGG Unequal Agent" ~ "experimental",
        studyID == "Control" ~ 'control'))

 data05 <- data05 %>% 
       mutate(treatments = case_when(
        studyID == "PT PGG Equal Agent" ~ "equal_agent",
        studyID == "PT PGG Equal Systemic" ~ "eaual_systemic",
        studyID == "PT PGG Unequal Systemic" ~ "unequal_systemic",
        studyID == "PT PGG Unequal Agent" ~ "unequal_agent",
        studyID == "Control" ~ 'control'))
```

### New Var: Equal vs. Unequal

Create variables that describe whether a respondent was in an equal or unequal condition. This will be used in our H2 analysis later on.

```{r}
      data05 <- data05 %>% 
       mutate(treat_parity = case_when(
         studyID == "PT PGG Equal Agent" ~ "equal",
         studyID == "PT PGG Equal Systemic" ~ "equal",
         studyID == "PT PGG Unequal Systemic" ~ "unequal",
         studyID == "PT PGG Unequal Agent" ~ "unequal",
         studyID == "Control" ~ 'control'))
```

### New Var: Systemic vs. Agent

Create variables that describe whether a respondent was in an Systemic or Agent condition. This will be used in our H3 analysis later on.

```{r}
      data05 <- data05 %>% 
       mutate(treat_power = case_when(
         studyID == "PT PGG Equal Agent" ~ "agent",
         studyID == "PT PGG Equal Systemic" ~ "systemic",
         studyID == "PT PGG Unequal Systemic" ~ "systemic",
         studyID == "PT PGG Unequal Agent" ~ "agent",
         studyID == "Control" ~ 'control'))
```

### New Var: Favored Groups

In the Unequal conditions, there were two roles: favored (saw multiplier) or unfavored (did not see multiplier). We create a new variable to split out those two experiences.

```{r}
      data_full <- data05 %>% 
       mutate(treat_alt = case_when(
         studyID == "PT PGG Equal Agent" ~ "equal_agent",
         studyID == "PT PGG Equal Systemic" ~ "equal_systemic",
         studyID == "PT PGG Unequal Systemic" & Favor_Reveal.0 == 1 ~ "unequal_systemic_certain",
         studyID == "PT PGG Unequal Systemic" & Unfavor_Reveal == 1 ~ "unequal_systemic_unfavor",
         studyID == "PT PGG Unequal Agent" & Favor_Reveal == 4  ~ "unequal_agent_certain",
         studyID == "PT PGG Unequal Agent" & Unfavor_Reveal_ == 4 ~ "unequal_agent_unfavor",
         studyID == "Control" ~ "control"))

```

### Subset data

Create subset dataset without pariticipants in "favored" version of Unequal conditions.

```{r}
     data_subset <- filter(data_full,
                           !treat_alt %in% c("unequal_agent_certain",
                                             "unequal_systemic_certain"))
```
### Naming
```{r}
 data_subset <- data_subset %>% 
       mutate(treat_formal = case_when(
        studyID == "PT PGG Equal Agent" ~ "Equal Agent",
        studyID == "PT PGG Equal Systemic" ~ "Equal Systemic",
        studyID == "PT PGG Unequal Systemic" ~ "Unequal Systemic",
        studyID == "PT PGG Unequal Agent" ~ "Unequal Agent",
        studyID == "Control" ~ 'Control'))
```

# Results

### Fig 2A: Boxplots for all conditions

```{r}

data_subset %>%
      ggplot(
      aes(x = as.factor(treat_formal),
      y = as.numeric(mean_cont))) +
      geom_boxplot() +
        xlab("Treatment Group") +
      ylab("Mean Contribution")+
      theme_classic() +
      geom_jitter(alpha = 0.3, width = .1)+
      stat_compare_means(label.x = 1.8, label.y = 22)+
      stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
             linetype="solid", size=1, color="red")


```

### Fig 2B. Sumarry statistics

```{r}
     
#stats

      sum_subset <- data_subset %>%                       
        group_by(treat_formal) %>% 
        summarize(
          count = n(),
          median = median(mean_cont),
          mean = mean(mean_cont),
          sd = sd(mean_cont))


#table
 stats_table <- sum_subset %>% 
        gt() %>% 
        tab_header(
          title = "Summary Statistics",
          subtitle = "Fair Side of Chance"
        ) %>% 
        fmt_number(
          columns = 2:5,
          decimals = 1,
          use_seps = FALSE) %>% 
      cols_label(
        treat_formal = md("**Condition**"),
        count = md("**Count**"),
        median = md("**Median**"),
        mean = md("**Mean**"),
        sd = md("**SD**")
        ) %>% 
      cols_align(
        align = "center",
        columns = everything())
 
 print(stats_table)
```

### Fig 3A: Parity Boxplot

```{r}
  data_subset %>%
        filter(treat_parity != "control") %>% 
        ggplot(
        aes(x = as.factor(treat_parity),
        y = as.numeric(mean_cont))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Mean Contribution")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")
```
### Fig 3B: Power Boxplot

```{r}
  data_subset %>%
        filter(treat_parity != "control") %>% 
        ggplot(
        aes(x = as.factor(treat_power),
        y = as.numeric(mean_cont))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Mean Contribution")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")
```
### Fig 3: Fairness Regression

```{r}

summary(lm(mean_cont ~ treat_formal + Fairness_1__1 + Fairness_2_1 + Fairness_3_1, data = data_subset))

fairness_reg <- lm(mean_cont ~ treat_formal + Fairness_1__1 + Fairness_2_1 + Fairness_3_1, data = data_subset)

plot_models(fairness_reg,
            rm.terms = c("treat_formalEqual Agent","treat_formalEqual Systemic","treat_formalUnequal Agent","treat_formalUnequal Systemic"),
            axis.labels = c("How multiplier was determined impacted fairness","Fairness Impacted contribution","Rules of the game were fair"),
            m.labels = c("Mean Contributions"),
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()

plot_models(fairness_reg,
            axis.labels = c("Q: How multiplier was determined impacted fairness","Q: Fairness Impacted contribution","Q: Rules of the game were fair","T: UnequalSystemic","T: Unequal Agent","T: Equal Systemic","T: Equal Agent"),
            m.labels = c("Mean Contributions"),
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()

 #axis.labels = c("Equal Agent","Equal Systemic","Unequal Agent","Unequal Systemic","Rules of the game were fair","Fairness Impacted contribution","How multiplier was determined impacted fairness"),
```

### Fig 4: Fairness scores

```{r}

# How fair were the rules of the game?
  data_subset %>%
        ggplot(
        aes(x = as.factor(treat_formal),
        y = as.numeric(Fairness_1__1))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Perceived Fairness of Game")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")

pairwise.wilcox.test(data_subset$Fairness_1__1, data_subset$treat_formal,
                          p.adjust.method="holm")

pairwise.wilcox.test(data_subset$Fairness_2_1, data_subset$treat_formal,
                          p.adjust.method="holm")

# How much did fairness impact decision making?

  data_subset %>%
        ggplot(
        aes(x = as.factor(treat_formal),
        y = as.numeric(Fairness_2_1))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Impact of Fairness on Cont Rate")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")

pairwise.wilcox.test(data_subset$Fairness_1__1, data_subset$treat_formal,
                          p.adjust.method="holm")

pairwise.wilcox.test(data_subset$Fairness_2_1, data_subset$treat_formal,
                          p.adjust.method="holm")

```


    
### Fig 5: Panel Regression Analysis

```{r}
# Creating long dataset

  data_long_subset <- data_subset %>% 
    pivot_longer(cols = c(cont1:cont8, ownContribution1, a1:sum1, share1:payoff8),
                 names_to = c(".value", "round"),
                 names_pattern = "(\\w+)(.)") 

# Adding the multiplier

 data_long_subset <- data_long_subset %>% 
     mutate(real_multilpier = case_when(
      round == 1 ~ '1.5',
      round == 2 ~ '5.15',
      round == 3 ~ '.21',
      round == 4 ~ '1.41',
      round == 5 ~ '1.55',
      round == 6 ~ '.48',
      round == 7 ~ '.56',
      round == 8 ~ '1.47',
     ))
   
  data_long_subset <- data_long_subset %>% 
     mutate(multilpier_last = case_when(
      round == 2 ~ '1.5',
      round == 3 ~ '5.15',
      round == 4 ~ '.21',
      round == 5 ~ '1.41',
      round == 6 ~ '1.55',
      round == 7 ~ '.48',
      round == 8 ~ '.56',
     ))
  
  #Creating partner contribution variable 
  
    data_long_subset <- data_long_subset %>% 
      mutate(partner_contribution = as.numeric(sum) - as.numeric(ownContribution))       
   
    data_long_subset <- data_long_subset %>% 
      group_by(ResponseId) %>%
      mutate(cont_partner_last = lag(partner_contribution, n=1, order_by=round))
      
    data_long_subset <- data_long_subset %>% 
      group_by(ResponseId) %>%
      mutate(last_cont = lag(ownContribution, n=1, order_by=round))

  #standarizing variables

  data_long_subset <- data_long_subset %>% 
   mutate(multiplier_std = (as.numeric(real_multilpier) /5.15)*20)  
  
  data_long_subset <- data_long_subset %>% 
    mutate(multiplier_last_std = (as.numeric(multilpier_last) /5.15)*20)
  
  #Creating experimental vs. control datasets
  
  data_long_subset_ctrl <- data_long_subset %>% filter(ctrlvsexp == "control")
    data_long_subset_exp <- data_long_subset %>% filter(ctrlvsexp == "experimental")


##Regression model

model_ctrl <- lmer(formula = as.numeric(ownContribution) ~ as.numeric(cont_partner_last) +  as.numeric(multiplier_std) + as.numeric(multiplier_last_std) + as.numeric(round) + (1|ResponseId), data = data_long_subset_ctrl)
 model_exp <- lmer(formula = as.numeric(ownContribution) ~  as.numeric(cont_partner_last) + as.numeric(multiplier_last_std) + as.numeric(round) + (1|ResponseId), data = data_long_subset_exp)
 
# Plotting regression models
plot_models(model_ctrl,
  rm.terms = c("as.numeric(multiplier_last_std)"),
  axis.labels = c("Round","Multiplier (Current)", "Partner Contribution (Last)"),         
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()
 
  
 plot_models(model_exp,
  axis.labels = c("Round","Multiplier (Last)", "Partner Contribution (Last)"),         
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()
 
 #Round by round plot
 
   data_long_subset %>% 
    ggplot(aes(x = as.numeric(round), y = as.numeric(cont), color = as.factor(studyID))) +
    geom_smooth(method = "loess", se = F) +
    xlab("Round") +
    ylab("Average Contribution") +
    labs(fill = "Condition")+
    scale_shape_manual(values = c("Control" = "grey85",
                                  "PT PGG Equal Agent" = "deepskyblue1",
                                  "PT PGG Equal Systemic"= "deepskyblue3",
                                  "PT PGG Unequal Agent" = "green1",
                                  "PT PGG Unequal Systemic" = "green3")) + theme_classic()
```
# RESULTS FROM FULL DATASET 

### Naming
```{r}
 data_full <- data_full %>% 
       mutate(treat_formal = case_when(
        studyID == "PT PGG Equal Agent" ~ "Equal Agent",
        studyID == "PT PGG Equal Systemic" ~ "Equal Systemic",
        studyID == "PT PGG Unequal Systemic" ~ "Unequal Systemic",
        studyID == "PT PGG Unequal Agent" ~ "Unequal Agent",
        studyID == "Control" ~ 'Control'))
```


### Fig 2A: Boxplots for all conditions

```{r}

data_full %>%
      ggplot(
      aes(x = as.factor(treat_formal),
      y = as.numeric(mean_cont))) +
      geom_boxplot() +
        xlab("Treatment Group") +
      ylab("Mean Contribution")+
      theme_classic() +
      geom_jitter(alpha = 0.3, width = .1)+
      stat_compare_means(label.x = 1.8, label.y = 22)+
      stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
             linetype="solid", size=1, color="red")


```

### Fig 2B. Sumarry statistics

```{r}
     
#stats

      sum_full <- data_full %>%                       
        group_by(treat_formal) %>% 
        summarize(
          count = n(),
          median = median(mean_cont),
          mean = mean(mean_cont),
          sd = sd(mean_cont))


#table
 stats_table <- sum_full %>% 
        gt() %>% 
        tab_header(
          title = "Summary Statistics",
          subtitle = "Fair Side of Chance"
        ) %>% 
        fmt_number(
          columns = 2:5,
          decimals = 1,
          use_seps = FALSE) %>% 
      cols_label(
        treat_formal = md("**Condition**"),
        count = md("**Count**"),
        median = md("**Median**"),
        mean = md("**Mean**"),
        sd = md("**SD**")
        ) %>% 
      cols_align(
        align = "center",
        columns = everything())
 
 print(stats_table)
```

### Fig 3A: Parity Boxplot

```{r}
  data_full %>%
        filter(treat_parity != "control") %>% 
        ggplot(
        aes(x = as.factor(treat_parity),
        y = as.numeric(mean_cont))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Mean Contribution")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")
```
### Fig 3B: Power Boxplot

```{r}
  data_full %>%
        filter(treat_parity != "control") %>% 
        ggplot(
        aes(x = as.factor(treat_power),
        y = as.numeric(mean_cont))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Mean Contribution")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")
```
### Fig 3: Fairness Regression

```{r}

summary(lm(mean_cont ~ treat_formal + Fairness_1__1 + Fairness_2_1 + Fairness_3_1, data = data_full))

fairness_reg <- lm(mean_cont ~ treat_formal + Fairness_1__1 + Fairness_2_1 + Fairness_3_1, data = data_full)

plot_models(fairness_reg,
            rm.terms = c("treat_formalEqual Agent","treat_formalEqual Systemic","treat_formalUnequal Agent","treat_formalUnequal Systemic"),
            axis.labels = c("How multiplier was determined impacted fairness","Fairness Impacted contribution","Rules of the game were fair"),
            m.labels = c("Mean Contributions"),
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()

plot_models(fairness_reg,
            axis.labels = c("Q: How multiplier was determined impacted fairness","Q: Fairness Impacted contribution","Q: Rules of the game were fair","T: UnequalSystemic","T: Unequal Agent","T: Equal Systemic","T: Equal Agent"),
            m.labels = c("Mean Contributions"),
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()

 #axis.labels = c("Equal Agent","Equal Systemic","Unequal Agent","Unequal Systemic","Rules of the game were fair","Fairness Impacted contribution","How multiplier was determined impacted fairness"),
```

### Fig 4: Fairness scores

```{r}

# How fair were the rules of the game?
  data_full %>%
        ggplot(
        aes(x = as.factor(treat_formal),
        y = as.numeric(Fairness_1__1))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Perceived Fairness of Game")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")

pairwise.wilcox.test(data_full$Fairness_1__1, data_full$treat_formal,
                          p.adjust.method="holm")

pairwise.wilcox.test(data_full$Fairness_2_1, data_full$treat_formal,
                          p.adjust.method="holm")

# How much did fairness impact decision making?

  data_full %>%
        ggplot(
        aes(x = as.factor(treat_formal),
        y = as.numeric(Fairness_2_1))) +
        geom_boxplot() +
          xlab("Treatment Group") +
        ylab("Impact of Fairness on Cont Rate")+
        theme_classic() +
        geom_jitter(alpha = 0.3, width = .1)+
          stat_summary(fun=mean, geom="errorbar", aes(ymax=..y..,ymin=..y..),
               linetype="solid", size=1, color="red")

pairwise.wilcox.test(data_full$Fairness_1__1, data_full$treat_formal,
                          p.adjust.method="holm")

pairwise.wilcox.test(data_full$Fairness_2_1, data_full$treat_formal,
                          p.adjust.method="holm")

```


    
### Fig 5: Panel Regression Analysis

```{r}
# Creating long dataset

  data_long_full <- data_full %>% 
    pivot_longer(cols = c(cont1:cont8, ownContribution1, a1:sum1, share1:payoff8),
                 names_to = c(".value", "round"),
                 names_pattern = "(\\w+)(.)") 

# Adding the multiplier

 data_long_full <- data_long_full %>% 
     mutate(real_multilpier = case_when(
      round == 1 ~ '1.5',
      round == 2 ~ '5.15',
      round == 3 ~ '.21',
      round == 4 ~ '1.41',
      round == 5 ~ '1.55',
      round == 6 ~ '.48',
      round == 7 ~ '.56',
      round == 8 ~ '1.47',
     ))
   
  data_long_full <- data_long_full %>% 
     mutate(multilpier_last = case_when(
      round == 2 ~ '1.5',
      round == 3 ~ '5.15',
      round == 4 ~ '.21',
      round == 5 ~ '1.41',
      round == 6 ~ '1.55',
      round == 7 ~ '.48',
      round == 8 ~ '.56',
     ))
  
  #Creating partner contribution variable 
  
    data_long_full <- data_long_full %>% 
      mutate(partner_contribution = as.numeric(sum) - as.numeric(ownContribution))       
   
    data_long_full <- data_long_full %>% 
      group_by(ResponseId) %>%
      mutate(cont_partner_last = lag(partner_contribution, n=1, order_by=round))
      
    data_long_full <- data_long_full %>% 
      group_by(ResponseId) %>%
      mutate(last_cont = lag(ownContribution, n=1, order_by=round))

  #standarizing variables

  data_long_full <- data_long_full %>% 
   mutate(multiplier_std = (as.numeric(real_multilpier) /5.15)*20)  
  
  data_long_full <- data_long_full %>% 
    mutate(multiplier_last_std = (as.numeric(multilpier_last) /5.15)*20)
  
  #Creating experimental vs. control datasets
  
  data_long_full_ctrl <- data_long_full %>% filter(ctrlvsexp == "control")
    data_long_full_exp <- data_long_full %>% filter(ctrlvsexp == "experimental")


##Regression model

model_ctrl <- lmer(formula = as.numeric(ownContribution) ~ as.numeric(cont_partner_last) +  as.numeric(multiplier_std) + as.numeric(multiplier_last_std) + as.numeric(round) + (1|ResponseId), data = data_long_full_ctrl)
 model_exp <- lmer(formula = as.numeric(ownContribution) ~  as.numeric(cont_partner_last) + as.numeric(multiplier_last_std) + as.numeric(round) + (1|ResponseId), data = data_long_full_exp)
 
# Plotting regression models
plot_models(model_ctrl,
  rm.terms = c("as.numeric(multiplier_last_std)"),
  axis.labels = c("Round","Multiplier (Current)", "Partner Contribution (Last)"),         
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()
 
  
 plot_models(model_exp,
  axis.labels = c("Round","Multiplier (Last)", "Partner Contribution (Last)"),         
  show.values = FALSE, show.p = FALSE, p.shape = TRUE)+
  theme_cleveland()
 
 #Round by round plot
 
   data_long_full %>% 
    ggplot(aes(x = as.numeric(round), y = as.numeric(cont), color = as.factor(studyID))) +
    geom_smooth(method = "loess", se = F) +
    xlab("Round") +
    ylab("Average Contribution") +
    labs(fill = "Condition")+
    ggtitle("Contribution Per Round by Condition: Subset")+
    scale_shape_manual(values = c("Control" = "grey85",
                                  "PT PGG Equal Agent" = "deepskyblue1",
                                  "PT PGG Equal Systemic"= "deepskyblue3",
                                  "PT PGG Unequal Agent" = "green1",
                                  "PT PGG Unequal Systemic" = "green3")) + theme_classic()